\bf Landslide: \\ Systematic Dynamic Race Detection in Kernel Space

### 2012-05-18 futurework.tex
credit vail photo

\begin{figure*}[h]
	\begin{center}
	\includegraphics[width=0.75\textwidth]{wont-modify-vail.jpg}
	\end{center}
	\caption{Former members of Operating Systems course staff lament the difficulty involved in teaching students concurrency debugging skills.}
\end{figure*}

>>>>

\begin{figure*}[h]
	\begin{center}
	\includegraphics[width=0.75\textwidth]{wont-modify-vail.jpg}
	\end{center}
	\caption{Former members of Operating Systems course staff lament the difficulty involved in teaching students concurrency debugging skills.\textsuperscript{1}}
\end{figure*}
\footnotetext{Joshua Wise, Ben Blum, and Michael Sullivan at Vail, Colorado. Included with permission.}
